My title

### 2022-02-02 outputs/paper/paper.Rmd
dfesd

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Adam Labas aka atom-laboss
thanks: "Code and data are available at: https://github.com/adam-labas/starter_folder"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Adam Labas aka atom-laboss
thanks: "Code and data are available at: https://github.com/adam-labas/adam_labas_paper_1_opendatatoronto"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
